Homework 6

### 2019-11-12 hw6/MSimonsHW6.tex
Correcting 2c and 2d in hw6

\item
\begin{enumerate}
\item There are 4 different quadratic polynomial in $(\Z/2\Z)[x]$:
\[
x^2
\] \[
x^2 + 1
\] \[
x^2 + x
\] \[
x^2 + x + 1
\]
Let $f(x)$ be any quadratic polynomial in $(\Z/2\Z)[x]$.  We know that
if $f(x) = x^2$, then $f(x)$ is reducible because $0$ is a root.
If $f(x) = x^2 + 1$, then $f(x)$ is reducible because $1$ is a root.
If $f(x) = x^2 + x$, then $f(x)$ is reducible because $1$ is a root.
\\ \\
If $f(x) = x^2 + x + 1$, then $f(x)$ is irreducible because $f(x)$ has no roots
in $(\Z/2\Z)[x]$:
\[
f(0) = 0^2 + 0 + 1 = 1
\] \[
f(1) = 1^1 + 1 + 1 = 3 = 1
\]
\\
Therefore the only irreducible quadratic polynomial in $(\Z/2\Z)[x]$ is
$x^2 + x + 1$.

\item No, because $f(1) = 0$.
\item Yes, because $g(0) = g(1) = 1$.
\item Yes, because $h(0) = h(1) = 1$.

>>>>

\item
\begin{enumerate}
\item There are 4 different quadratic polynomial in $(\Z/2\Z)[x]$:
\[
x^2
\] \[
x^2 + 1
\] \[
x^2 + x
\] \[
x^2 + x + 1
\]
Let $f(x)$ be any quadratic polynomial in $(\Z/2\Z)[x]$.  We know that
if $f(x) = x^2$, then $f(x)$ is reducible because $0$ is a root.
If $f(x) = x^2 + 1$, then $f(x)$ is reducible because $1$ is a root.
If $f(x) = x^2 + x$, then $f(x)$ is reducible because $1$ is a root.
\\ \\
If $f(x) = x^2 + x + 1$, then $f(x)$ is irreducible because $f(x)$ has no roots
in $(\Z/2\Z)[x]$:
\[
f(0) = 0^2 + 0 + 1 = 1
\] \[
f(1) = 1^2 + 1 + 1 = 3 = 1
\]
\\
Therefore the only irreducible quadratic polynomial in $(\Z/2\Z)[x]$ is
$x^2 + x + 1$.

\item No, because $f(1) = 0$.
\item No, because $g(x) = x^5 + x^4 + 1 = (x^2 + x +1)(x^3 - x + 1)$.
\item Yes.  Since $h(x)$ does not have any roots, it is not divisible
by a polynomial with degree 1.  Therefore, it can only be the product
of an irreducible polynomial with degree 2 and an irreducible polynomial of
degree 3.  The only irreducible polynomial with degree 2 in
$\mathbb{Z}/2\mathbb{Z}$ in $x^2 + x + 1$.  Therefore, if $h(x)$ is reducible,
then it is divisible by $\mathbb{Z}/2\mathbb{Z}$ in $x^2 + x + 1$.  However,
$h(x)$ is NOT divisible by $\mathbb{Z}/2\mathbb{Z}$, so it must be irreducible.
